Scaling Automated Theory Exploration

### 2015-08-07 AI4FM/article.tex
Preparing to change

% Acknowledgements for colleagues, referees, ...
% ==============================================
\begin{acknowledge}
Thank you to my supervisor Katya Komendantskaya and members of the
\textsc{HipSpec} team at Chalmers University (Moa Johansson, Koen Claessen, Nick
Smallbone, Dan Ros{\'e}n and Irene Lobo Valbuena) for useful discussions of these
ideas.
\end{acknowledge}

>>>>

% Acknowledgements for colleagues, referees, ...
% ==============================================
\begin{acknowledge}
Thank you to the \textsc{HipSpec} team at Chalmers University (Moa Johansson,
Koen Claessen, Nick Smallbone, Dan Ros{\'e}n and Irene Lobo Valbuena) for useful
discussions of these ideas.
\end{acknowledge}
